Farley et al. 2024

### 2025-01-10 AT_2025.qmd
Update before pausing

# Pivot the data to be longer
AT_2025_Long <- AT_2025_data |>
	pivot_longer(cols = -gene_name,
				names_to = c(".value", "Sample"),
				names_pattern = "^(logFC|pvalue|hit_annotation)_(.+)$")

@@

# Applies the ID column to the PE results
AT_2025_ranked_PE <- AT_2025_Long |>
    arrange(logFC) |>
	filter(Sample == "PE") |>
	mutate(ID = ID)

# Applies the ID column to the PA results
AT_2025_ranked_PA <- AT_2025_Long |>
    arrange(logFC) |>
	filter(Sample == "PA") |>
	mutate(ID = ID)

@@

filter_select(id = "Sample",
				label = "Functional probe used in pulldown:", 
				sharedData = AT_2025_Long_reactive,
				group = ~Sample)

>>>>

# Pivot the data to be longer
AT_2025_Long <- AT_2025_data |>
	pivot_longer(cols = -gene_name,
				names_to = c(".value", "LipidProbe"),
				names_pattern = "^(logFC|pvalue|hit_annotation)_(.+)$")

@@

# Applies the ID column to the PE results
AT_2025_ranked_PE <- AT_2025_Long |>
    arrange(logFC) |>
	filter(LipidProbe == "PE") |>
	mutate(ID = ID)

# Applies the ID column to the PA results
AT_2025_ranked_PA <- AT_2025_Long |>
    arrange(logFC) |>
	filter(LipidProbe == "PA") |>
	mutate(ID = ID)

@@

filter_select(id = "LipidProbe",
				label = "Functional probe used in pulldown:", 
				sharedData = AT_2025_Long_reactive,
				group = ~LipidProbe)

### 2025-01-10 SF_2024.qmd
Update before pausing

```{r setup, echo=FALSE, include=FALSE}

>>>>

```{r setup, echo=FALSE, include=FALSE}
source("ggplot_styles.R")

SF_2024_data <- readr::read_csv("DataTables/SF_ACS-ChemBio_2024_Limma_results_V3.csv")

SF_2024_data_2 <- SF_2024_data |>
	select(gene_name, keep_Huh7, comparison, logFC, pvalue, hit_annotation) |>
	filter(keep_Huh7 == TRUE) |>
	select(-keep_Huh7) |>
	glimpse()

print(head(SF_2024_data_2))
```
